\begin{rtext}
    \subhead{ECE468/ECE568: Computer Security.} This is a new senior level course developed for the undergraduate curriculum at the University of Toronto in 2006.  The course covers practical and theoretical aspects of computer security to help senior students prepare for security related employment and/or graduate studies.  At the time, there were few appropriate text books for the material so I developed all material for the course.  A comprehensive set of lecture notes were made in the form of slides and is distributed to the students each year in lieu of a course text.
    
    The initial course material contained 4 written assignments, 4 major programming labs introducing students to software vulnerabilities and network security, and lecture notes.  The labs involved the development and installation of a virtual machine infrastructure on the undergraduate computing labs (ECF), as well as a fake website with security vulnerabilities that students could use to practice identifying and fixing security problems.  
    
    Materials developed in this course were incorporated into the course ``Introduction to Information Security'' (CS347) at the University of Toronto Mississauga Campus.  The course was upgraded into a 500 level course in 2011, thus making it available to Graduate students who did not have such a course available to them at their
    undergraduate institution.
    
    In 2015, the course material was updated to include more web security content, federated identity mobile security, cloud security and block chains to reflect newer concepts in computer security.  
    
    \subhead{Curriculum Development.} I participated in an undergraduate curriculum review conducted in 2004-2005.
\end{rtext}