\textbf{Associate Director, Data Sciences Institute, University of Toronto (2022-):} I managed Thematic Programs and ran the Emerging Data Sciences and Data Access Granting programs for the Data Sciences Institute at the University of Toronto.

\textbf{Research Lead, Schwartz Reisman Institute for Technology and Society (2020-):} I helped oversee the founding and research operation of the newly formed Schwartz Reisman Institute, a multi-disciplinary institute whose mission is to deepen our knowledge of technologies, societies, and what it means to be human by integrating research across traditional boundaries.

\textbf{Associate Chair, Graduate Studies (2012-2015):}  As Associate Chair, I headed up several major initiatives to improve the graduate program in the ECE department at the University of Toronto.  First, the growth in the size of our course-based Masters of Engineering program (MEng), demanded major changes to the running of the program.  During my tenure from 2012-2015, the number of MEng applicants grew from 200 to over 450.  I created a committee structure and an admissions process to fairly and objectively rate each applicant.  Second, the number of graduate courses and graduate student had grown over the last few years.  I conducted a curriculum review to identify and remove dormant courses, and identify redundancies, as well as gaps in the graduate curriculum.  Finally, in response to the large number of research stream students, I initiated development of an online graduate student tracking and information database.
